---
title: "math250_nov5_ArleneSMedina"
format: html
embed-resources: true
---
# Problem 1 
## The first two problems in this set refer to the ISLR2::Carseats set, which includes simulated sample data for 400 stores selling a particular brand of child carseat. We view this data as a simple random sample from a larger population.

## Does this data provide evidence against the company’s claim that the average price of their own seats is $110? Follow all best practices from class, including hypotheses, a relevant visualization, and a conclusion in non-technical language.
```{r}
library(ISLR2)
library(tidyverse)
glimpse(Carseats$Price)
```


## Hypthesis: From just taking a quick glance at it's 400 rows and 11 respective columns. I would say that the average price of the carseats is more than $110 per seat. As well as from past/real life situations. 
```{r}
summary(Carseats$Price)
```

## Visualization that supports output of summary: 
```{r}
ggplot(Carseats,aes(x = Price)) + 
  geom_histogram(color = "black",
                 fill = "grey",
                 bins = 25) + #so that the message error could be removed 
  geom_vline(aes(xintercept = 115.8, #previously mentioned in 
             color = "Actual Carseat Mean"))+ 
  geom_vline(aes(xintercept = 110, #previously mentioned in 
             color = "Firms Mean Claim"))+ 
  labs(title = "Carseat Price Range",
       x = "Price (dollars)", 
       color = "Carseats Mean") +
  theme_minimal()
```

