---
title: "math250_nov5_ArleneMedina"
format: html
---
#Problem 1 
#The first two problems in this set refer to the ISLR2::Carseats set, which includes simulated sample data for 400 stores selling a particular brand of child carseat. We view this data as a simple random sample from a larger population.
#Does this data provide evidence against the company’s claim that the average price of their own seats is $110? Follow all best practices from class, including hypotheses, a relevant visualization, and a conclusion in non-technical language.
```{r}
library(ISLR2)
library(tidyverse)
glimpse(Carseats$Price)
```

# Hypthesis: From just taking a quick glance at it's 400 rows and 11 respective columns. I would say that the average price of the carseats is more than $110 per seat. As well as from past/real life situations. 
```{r}
summary(Carseats$Price)
```

#Visualization that supports output of summary: 
```{r}
ggplot(Carseats,aes(x = Price)) + 
  geom_histogram(color = "black",
                 fill = "grey") +
  geom_vline(aes(xintercept = 115.8, #previously mentioned in 
             color = "Actual Carseat Mean"))+ 
  geom_vline(aes(xintercept = 110, #previously mentioned in 
             color = "Firms Mean Claim"))+ 
  labs(title = "Carseat Price Range",
       x = "Price (dollars)", 
       color = "Carseats Mean") +
  theme_minimal()
```

#Conclusion (non-technical language): We can determine that the firms carseats average is more than what they claim it to be. Meaning that the carseats are on average more expensive than $110 that they claim. Instead they're 115.8. 

#Problem 2: 
#Compute a level 90% confidence interval for the mean competitor price in the population from which this sample is drawn. What is the sample mean? What is the margin of error?
```{r}
mean_competition_price <- mean(Carseats$CompPrice) #Learned from Professors vid "Confidence Intervals in R" 
new_t_test <- t.test(Carseats$CompPrice, conf.level = .90)
new_t_test #From the output we learned: 126.2391 - 124.975
```
#The Marginal Error is: 1.2641
#The Sample Mean is : 124.975

#Problem 3: Create a table with counts of penguin species and home islands in the penguins set. Include marginal counts in the table. 
```{r}
t <- table(penguins$species, penguins$island)
t
addmargins(t) #Adding marginal counts
```
#Problem 4: Push solution to Github page, including both both the Quarto Source and the rendered html. Use file names of the form, and provide clickable link. 